### 2017-12-24 article.tex
rivising section 9

The current ratio measures an entity’s ability to repay its short-term obligations. .
The decreasing current ratio also implies that the Group are under pressure to pay the creditor back. Some potential creditors may doubt whether the Group in question would be able to pay off its obligations if they came due at that point.

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}
The quick ratio reflects the ability of a company to repay its short-term obligations with its more liquid assets. It is a more stringent measure as compared to the current ratio. The 13.4\% increase in FY 2007 indicates a better capability of the Group in meeting its current liabilities with its available liquid assets. This increase was effected mainly due to the large increase in cash and cash equivalents coupled with the drop in current liabilities.

@@

@@

\subsection{Inventory Turnover}
Based on the data of JD.com, Inc. consolidated balance sheet\footnote{See JD.com, Inc. annual report 2016, Page F-3 and JD.com, Inc. annual report 2015, Page F-3} and consolidated statements of operations and comprehensive loss\footnote{See JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

@@

>>>>

The current ratio is a liquidity ratio that measures a company's ability to pay short-term and long-term obligations. To gauge this ability, the current ratio considers the current total assets of a company (both liquid and illiquid) relative to that company’s current total liabilities.

The decreasing current ratio also implies that the Group are under pressure to pay the creditor back. Some potential creditors may doubt whether the Group in question would be able to pay off its obligations if they came due at that point.

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&(37.46\%)&(25.51\%)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}
The quick ratio reflects the ability of a company to repay its short-term obligations with its more liquid assets.

@@

The gross profit ratio is important because it shows management and investors how profitable the core business activities are without taking into consideration the indirect costs. This gives investors a key insight into how healthy the company actually is. For instance, a company with a seemingly healthy net income on the bottom line could actually be dying. The gross profit percentage could be negative, and the net income could be coming from other one-time operations. The company could be losing money on every product they produce, but staying a float because of a one-time insurance payout.

@@

Gross profit increased 1.77 percents in fiscal year 2016. It shows the Group can produce and sell its products more efficiently.

\subsection{Inventory Turnover}

The Inventory turnover is a measure of the number of times inventory is sold or used in a time period such as a year. The equation for inventory turnover equals the cost of goods sold divided by the average inventory.

Based on the data of JD.com, Inc. consolidated balance sheet\footnote{See JD.com, Inc. annual report 2016, Page F-3 and JD.com, Inc. annual report 2015, Page F-3} and consolidated statements of operations and comprehensive loss\footnote{See JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

@@

Gross profit decreased 0.768 in fiscal year 2016. It suggests weaker sales and therefore excess inventory. The Group sold inventories rather slower compared to the fiscal year 2015.
